
%As commerce has increasingly moved to the Internet, 

Over \$514 billion dollars worth of transactions now occur online \citep {ecommerce}. A growing sector of online commerce is peer-to-peer (P2P) platforms, in which two people interact directly as buyers and sellers, rather than making purchases at a brick-and-mortar store or visiting the website of a business. Sharing economy businesses have sprung up as the newest incarnation of the P2P model, allowing members to buy or share certain goods and services through a central platform. Buyers can bike, car, or apartment share by simply renting the product for a short period of time from the seller. 

Unlike in traditional markets, participants on these platforms most often do not meet in person before agreeing to a transaction. Moreover, strangers on these platforms are not likely to have the reputational safety of a brick-and-mortar store, and thus have a harder time credibly guaranteeing the quality of their product. These factors contribute to a higher perceived risk of transacting online. 

As a result, many sharing economy platforms have instituted measures to mitigate this risk. Most have user profiles and encourage users to post their names and photos, as well as descriptions of themselves and their products, to bolster credibility. Platforms often solicit reviews from previous buyers that are posted alongside the product, or on the seller's profile, to aid future buyers by increasing transparency and thereby encouraging transactions. However, the presence of identifiable information about a person’s demographic characteristics gives rise to the possibility of discrimination. Indeed, a growing body of research indicates that P2P market participants discriminate online in much the same ways as they do in traditional markets. 

This paper leverages the standardization provided by P2P marketplaces to measure the effect of host race on listing price on the world's biggest short-term rental platform, Airbnb. Using data scraped from the Airbnb website, I code the demographic information of 70,000 Airbnb hosts throughout the country. I find that non-White hosts, both male and female, have lower prices than White hosts on the platform, and test different hypotheses to explain this disparity.  

Previous literature has examined discrimination against Airbnb hosts in various small samples \citep{edelman, wang, kakar}. All three studies have found evidence of a price disparity for minority hosts of different races. The first study of this kind estimated that non-Black hosts have higher prices than Black hosts in New York City \citep{edelman}. \cite{wang} and \cite{kakar} did not find lower prices for Black hosts, but did find evidence of a price disparity for Asian hosts in the Bay Area. 

The comprehensiveness of mitigating controls varies enormously in this literature. \cite{wang} and \cite{edelman} were limited by the sparse listing information available on the Airbnb website (Airbnb has since added more comprehensive listing details). For instance, \cite{edelman} only control for a few property characteristics, the quality of the host's reviews, and a measure of the reliability of the host. However, there are still many other observables, such as the type of listing, and unobservables, such as the quality of the host themselves, which could differ by race and contribute to variation in prices.

In sum, no study has measured a price disparity in a large, representative, multi-city sample of Airbnb listings. There exists no research conclusively showing whether or not minority hosts face a price disparity in the nationwide Airbnb market, whether the price disparity differs in magnitude by city, or whether hosts of a certain race fare better in some cities and worse in others. This paper seeks to fill these gaps. 

I build on the existing literature in the following ways. First, I bring more robust data than existing studies to the question. My sample includes seven large urban centers that cover each geographic region in the United States. Second, I control for a comprehensive set of confounders that includes all information available to a guest on the listing page. To account for unobservable differences in host quality, I use machine learning techniques to analyze the descriptions on listing pages. These controls comprise the rest of the observable information on the listing page that could influence a demand for that listing. Third, I code the demographic characteristics of reviewers in Chicago to examine whether or not minority hosts have worse reviews, and whether review quality differs by the reviewer's race. Fourth, I use this review quality data, and proxies for the quantity demanded of a listing, to test hypotheses that could explain the price disparity. 

I find a negative effect of minority host race on listing prices on Airbnb. My point estimates indicate that this price disparity between White and non-White hosts is widest for Asian hosts. The prices of Asian hosts of both sexes are roughly 4.5\% lower than White male hosts who own a property in a similar location with similar characteristics. The second biggest effect is for Black male hosts, whose listed price is lower by around 3\%.%
	\footnote{This effect is statistically significant at the p $<$ .001 level for Asian female hosts, and the p $<$ .01 level for Asian and Black male hosts. For Hispanic hosts and Black female hosts, the effect is small, around 2\%, and is not statistically significant.} 
These estimates are smaller than those measured by the previous studies. This fact is unsurprising, as it is unlikely that we would measure the same disparity when there are important structural differences between this paper and previous literature in the sample, sample size, and empirical approach. ADD OSTER HERE. 

There are two theoretical reasons that could explain why minority hosts systemically charge lower prices than White hosts for listings of the same quality. The first is that low prices are a response to lower demand for their listings. Throughout the paper, I refer to this as a demand shift, or a demand effect. Statistical discrimination as laid out by \cite{becker} is one explanation for lower demand. In the Airbnb market, if a guest is discriminating, then given two comparable listings they would be willing to pay more to avoid staying in the listing owned by a minority host. Responding to (or anticipating) this lower demand, minority hosts rationally post a lower price. 

The second theoretical reason for a lower price is a shift right in the supply curve. I refer to this as a supply shift, or supply effect. A supply shift could be due to a lower marginal cost of operating the listing for minority hosts relative to White hosts. For instance, minority hosts could charge a lower price for their listing because it is marginally cheaper for them to operate a similar listing relative to a White host. Since Black and Hispanic workers tend to earn less than their White counterparts, even for the same amount of education, they may have a lower opportunity cost of time \citep{wages}. They would therefore have a lower marginal cost of managing their listing, and so would set lower prices than White hosts with comparable listings.  

Basic microeconomic theory states that the quantity demanded in a market can help differentiate between a demand versus a supply effect. A lower price and lower quantity demanded points to a demand shift, whereas a lower price but higher quantity demanded points to a supply shift. In the context of Airbnb, the true measure of a listing's quantity demanded would be its number of bookings. However, I do not observe this value in my data. Throughout my analysis, I therefore use two proxies for the number of bookings: the number of reviews of a listing and its vacancy rate. I use these two measures of quantity demanded to address whether the price disparity is caused by a demand or supply effect. %This is important because knowing both quantity demanded and price allows me to test whether the price disparity is due to a racially-induced demand shift in guest preferences, an empirical finding which would be consistent with discrimination. If this is the case, I would observe in the data that despite lower prices, minority listings have lower quantity demanded. However, lower prices could also signal a supply shift, in which case minority hosts would have higher quantity demanded. 

My first measure of quantity demanded is the number of reviews. I find that Black hosts, White female hosts, and Asian female hosts have 5-10\% fewer reviews than White hosts for a listing that has spent the same amount of time on the market. Effects for all other host categories are slightly negative, but not statistically significant.%
	\footnote{This conclusion is only salient if the total number of reviews is a reasonable proxy for the demand of a listing. Yet, one can imagine that if reviewers systematically under-review minority hosts relative to White hosts, these groups would have lower numbers of reviews that do not necessarily represent a lower quantity demanded. There is no way to tell apart these mechanisms in my data. A recent study found that reviews left by hosts on guests’ pages can significantly reduce discrimination and render acceptance rates of guests with White-sounding names and African American-sounding names statistically indistinguishable \citep{cui}, but it remains unknown whether or not reviewers discriminate against minorities in leaving reviews \citep{ye}. If reviewers systematically under-review minority hosts, this itself could be evidence of discrimination. My working assumption is that even if not every guest leaves a review, the review proportion is similar across host race, and a lower number of reviews therefore indicates a real difference between quantity demanded of minority hosts and White hosts.}

One potential explanation for a lower number of reviews is that a minority host might make their listing available to guests less frequently than a White host. A host controls how many days of the month they offer their listing for rent via an availability calendar on the listing page. When a guest books their listing, the booked days disappear from the availability calendar. Therefore, the availability is actually a measure of the vacancy rate for the listing. If a host has a fewer reviews, perhaps this is because they offer their listing for fewer days of the month. To test this, I regress a listing's vacancy rate on host race. Results show that contrary to this hypothesis, the listings of Black hosts stay vacant 1.5 to 2.5 days per month \textit{longer} than the listings of White hosts. The listings of White female hosts and Asian female hosts, on the other hand, are vacant slightly less frequently than listings owned by White hosts, meaning that higher vacancy rate could be driving lower review numbers.

In sum, no minority host group has a higher number of reviews than White hosts. This fact provides suggestive evidence that minority hosts' quantity demanded on Airbnb is \textit{at worst} not higher than those of White hosts. For minority hosts who have a statistically significant lower number of reviews, the potential explanations differ. For  Black hosts, both measures of quantity demanded tell the same story: that despite lower prices, the listings of Black hosts have fewer guests and stay vacant for longer. However, at least part of the lower number of reviews for Asian females and White females can be explained by differences in availability. 


%Another type of discrimination laid out by Becker is taste discrimination, in which people ``prefer" not to interact with certain groups. This type of taste discrimination that is based on a general dislike could show up in the reviews that are left on host profiles. If a guest stays with a host against whom they are prejudiced, they may leave a worse review or rating, a shorter review, or no review at all, than a comparable stay with a white host. 

A demand shift could also be caused by differences in review quality. Host race could drive differences in reviews because minority hosts are of worse quality, or because discriminatory guests rate minority hosts lower for the same quality of stay. If minority hosts have worse reviews on their listing page, it might decrease demand by discouraging future guests. To this end, I estimate the effect of host race on review quality. I use the race and gender of the reviewer and the host to compare the sentiment (how favorable or unfavorable the review is) of the reviews that guests leave for White and for minority hosts.%
	\footnote{Since it required hand-coding, demographic information of the reviewers is only available for a randomly-chosen subset of hosts in Chicago.} 
I do not observe that minority hosts uniformly have lower quality reviews. Rather, there is either no statistically significant difference in review quality, or the effect depends on the demographics of the reviewer and host. Column 1 of Table \ref{table:reviewer_demographics} shows that Black and Hispanic males have reviews that are .1 -- .2 standard deviations worse than their White male hosts, significant at the p $<$ .01 level. Interestingly, there appears to be little within-race preference between reviewers and hosts, though many of the estimates are unreliable due to small counts in some of the reviewer-host pairings. %Taken as a whole, sentiment analysis suggests that Black and Hispanic men have lower quality reviews than their White male counterparts. 

\subsection{About Airbnb} 
\label{about}

Airbnb is a sharing economy platform founded in 2008 that allows people to rent out their apartment, house, or a single room to short-term lodgers. As of 2017, it had more than 3 million listings, more than Marriott's 1.2 million rooms worldwide \citep{aboutus}. Just like traditional hotel chains, guests on Airbnb can browse listings by city and property type, and book a stay based on prices, location, past reviews, pictures of the listing, size, and amenities. Unlike traditional hotel chains, however, hosts create a profile for themselves and a page for each listing they are renting. Each listing page includes the name and picture of the host, the reviews left by previous guests, and those guests' profile pictures. Guests can therefore infer demographic information about the host through a host's picture and name, creating the opportunity for discrimination. Figures \ref{fig:listing}-\ref{fig:property} present screenshots of a listing in a Chicago neighborhood, illustrating some of the information that would be available to a potential guest. %Figures \ref{fig:reviewinfo} - \ref{fig:location} display an example of reviews, a sample host profile, and sample location maps, and can be found in the Appendix.


\subsection{Previous Literature} 
\label{lit}

\textbf{Theoretical foundation}

\cite{becker} proposed the idea that discrimination against a group is reflected in the prices that that group charges in a particular market, be it labor or products. In the Airbnb market, Becker's market discrimination would be reflected in the price that the guest (buyer) pays to the host (seller) to stay with them. If the guest is discriminating, then given two comparable listings, they would choose not to stay in the one owned by a minority host. Responding to (or anticipating) a lower demand, hosts in minority groups rationally post a lower price and, despite this, face a lower quantity demanded. 

This type of market discrimination rests on the idea that groups who are discriminated against face lower demand in the market, which drives down their prices. But ex ante, it is unclear if a hypothetical price disparity measured between minority and White hosts is a result of a shift in the supply or demand of listings. There could be multiple explanations for a lower supply curve rather than demand curve. For instance, minority hosts could charge a lower price for their listing because it is cheaper for them, on the margin, to operate a similar listing relative to a White host. Since Black and Hispanic workers tend to earn less than their White counterparts, even for the same amount of education, they may have a lower opportunity cost of time \citep{wages}. Minority hosts would therefore have a lower marginal cost of managing their listing, and so would choose to set lower prices than White hosts with comparable listings. If the price disparity was due to these marginal cost differences, then the quantity demanded of minority hosts' listings should be higher than those of White hosts. 

Basic microeconomic theory says that we can test this by examining the quantity demanded. If prices are lower because the supply curve is lower, then minority hosts would have a higher quantity demanded. Conversely, if the prices are lower because the demand curve is lower -- which would be in line with the presence of discrimination -- then the quantity demanded should be lower than it is for White hosts. 

Becker was concerned with discrimination arising from face-to-face interactions between minority and majority groups. Since then, there has been a large amount of research indicating that Becker's theory holds for people participating in online markets for labor, lending, rental, and products. In these cases, participants simply bring their prejudices online and use names and photos to discriminate. Next, I detail the research that explores how the theory of discrimination plays out in both traditional and online markets. 


%Becker explains, ``If someone has a `taste for discrimination', he must act as if he were willing to forfeit income in order to avoid certain transactions; it is necessary to be aware of the emphasis on the words `as if'" (Becker 16).While market discrimination harms the discriminated group because it lowers their wages, taste discrimination can also harm the person discriminating, since they might now be paying more for the same good or service - whether in opportunity cost or price -  because they prefer not to interact with the discriminated group. 
%Another type of discrimination laid out by Becker is taste discrimination, in which people ``prefer" not to interact with certain groups. This type of taste discrimination that is based on a general dislike could show up in the reviews that are left on host profiles. If a guest stays with a host against whom they are prejudiced, they may leave a worse review or rating, a shorter review, or no review at all, than a comparable stay with a white host. 

\vspace{5mm}
\textbf{Research on discrimination in traditional housing markets}

African-Americans experience pervasively worse outcomes in the housing market as a result of historic and current racial discrimination \citep{krysan}. Even after the gains during the Civil Rights Era, such as the landmark Fair Housing Act of 1968, discrimination in the housing market has been widely documented by social scientists. African-American renters are told that there are 30\% fewer available housing units than White renters \citep{yinger1}. African-American families face higher barriers when raising capital to purchase a home \citep{pope}. E-mails sent to landlords from home-seekers with typically African-American names receive lower response rates than emails sent by those with names commonly associated with White people \citep{hanson}.

Economists have primarily studied discrimination against African-American tenants. There is little research on the other side of the market -- when African-Americans are supplying, rather than demanding, housing. Because property ownership cannot be randomized, it is difficult to disentangle true discrimination from systematic differences in the housing owned by African-Americans and White landlords.%
	\footnote{One would also expect Black landlords to fare worse than White landlords in this area as well. Properties owned by African-Americans tend to be less expensive than those owned by White Americans. The average Black household still has less mean wealth than a White household \citep{oliver}. Even middle-class Black and Hispanic households still live in neighborhoods with median incomes similar to those of very poor White neighborhoods \citep{reardon}.} 
Some studies have found evidence that African-American homeowners are more likely to be targeted by subprime loans \citep{foreclosure} or pay more than White people for similar housing \citep{bayer, myers}, but few studies have a credible identification strategy to separate discrimination from correlated observables. 

%Some studies have found correlatory evidence of discrimination against African-American homeowners, but none have a credible mechanism to identified discrimination from other factors. For instance, the spike in subprime lending and the ensuing foreclosure crisis was found to be causally linked to residential segregation, and evidence suggests that specifically Black residential dissimilarity and spatial isolation were important predictors of foreclosures across U.S. metropolitan areas \citep{foreclosure}.



\vspace{5mm}
\textbf{Research on discrimination in P2P online commerce}

\cite{doleac} examined the effect of apparent race on market outcomes when selling an iPod on various online marketplaces. In some pictures, a dark-skinned hand was holding the iPod, signaling a Black seller, while in others, a light-skinned hand was holding the iPod, signaling a White seller. Hands which indicate a Black seller received 18\% fewer and 11\% lower offers than White sellers. Furthermore, bidders were less likely to include their name in offers made to Black sellers. \cite{pope} found that in a P2P lending market (Prosper.com) demographic characteristics conveyed through pictures and text significantly affected loan terms for Black borrowers. Black borrowers were 25\% to 35\% less likely to receive loans than White borrowers with similar credit profiles, and loans received by Black borrowers had an interest rate 60 to 80 basis points higher than White borrowers.

In sharing economies, a similar pattern occurs. \cite{knittel} explored the effect of race on market outcomes in rideshare platforms. These platforms provide rider information such as the first name, photo, and rating to drivers before (Lyft) or at (Uber) the time of ride acceptance. The authors ordered 1,500 Uber and Lyft trips to measure the impact of rider race on fare and wait times, varying the apparent race of the rider in user photos, as well as degree to which riders’ names were distinctively Black. Uber riders who use distinctively Black names experience up to 35\% longer wait times and more frequent cancellations than riders who use distinctively White names, especially for males in low population density areas.

These studies suggest that users of online platforms use visual and textual information to transfer their racial biases from the real world into the online world. Though it is difficult to confirm whether these biases stem from statistical or taste-based discrimination, they provide evidence that P2P market participants like Uber drivers, Prosper lenders, and iPod buyers use racial information in their market decisions. 



\vspace{5mm}
\textbf{Research on Airbnb generally}

The appeal of easily accessible, affordable, and short-term peer-to-peer accommodation has led many travelers to opt for Airbnb over a hotel stay under the perception that a number of Airbnb attributes outperform those of traditional hotels \citep{guttentag}. This pattern has become increasingly prevalent in popular tourist cities, where Airbnb offers cheaper lodging closer to city centers than hotels \citep{gutierrez}. However, the influx of tourists into residential areas and lack of industry regulation on Airbnb are quickly becoming causes of economic and social concern. \cite{leong} investigate the legal ramifications of not subjecting Airbnb to the same regulations as similar establishments. They note that the existing policies prohibiting public accommodations like hotels, restaurants, taxis, and retail businesses from discriminating against customers on the basis of characteristics such as race or religion have not yet evolved to apply to Airbnb, which exposes the platform to the risk of intentional bias and discrimination \citep{leong}. 

%The rise of the Airbnb sharing economy has garnered interest in its microeconomic impacts and policy implications. \cite*{mao} investigated the effects of Airbnb on hotel prices in 221 different counties across the U.S. and found that the expansion of Airbnb into counties led to drops in hotel room demand, but also reduced unemployment in industries complementary to Airbnb’s core business, such as administration, support and waste management, and accommodation and food services. \cite*{barron} found evidence that a 10\% increase in Airbnb listings resulted in a 0.42\% increase in rents of residential properties, and a 0.76\% increase in house prices. These effects were found to be more pronounced in areas with smaller shares of occupiers who owned their place of residence, meaning that not only was the rent increase larger in these areas, but it also affected a larger share of those areas’ residents.



\vspace{5mm}
\textbf{Research on discrimination in Airbnb}

This study builds primarily on research done by \cite{edelman}, \cite{wang}, and \cite{kakar}. 

\cite{edelman} was the first study to explore the effect of Airbnb host race on the price of a listing using a sample of 3,800 New York City hosts. They use Amazon Mechanical Turk workers to identify the race of the host in Airbnb profile pictures. Controlling for a listing's location, its rating on various dimensions, and several variables related to the size of the listing, the researchers find evidence that non-Black hosts on Airbnb charge prices roughly 12\% higher than Black hosts. Since their study was conducted using data from 2012, when Airbnb was relatively new, the authors were able to include all of Airbnb's New York City listings in their sample. \cite{edelman} considered only Black hosts. They did not differentiate impact by gender, and were only able to control for a few property characteristics. 

Given these constraints, \cite{wang} and \cite{kakar} build on \cite{edelman}'s approach and apply it to study discrimination in the context of the San Francisco Bay Area. 

Wang et al. (2015) analyzed the impact of Asian host race on Airbnb prices in Oakland and Berkeley by scraping information on 100 hosts from the Airbnb website in those areas. They found that when controlling for the number of bedrooms, bathrooms, and maximum occupancy, Asian hosts earned \$90 (20\%) less than White hosts with similar rentals. 

The fact that a price disparity is estimated for both Black and Asian hosts, albeit in different contexts, is potentially informative about the mechanism behind discrimination in this context. The Black-White wealth gap is well-documented, large, and pervasive \citep{cfed, heywood, bayard, mason, chiteji, altonji, gittleman}. When considering discrimination against Black hosts, it is unclear if guests discriminate because they expect listings of lower quality (statistical discrimination) or if they simply do not want to stay with Black hosts (taste-based discrimination). By contrast, Asians in the United States have the highest incomes out of any ethnicity in the US \citep{income}. It is therefore unlikely that discrimination against Asian hosts would be statistical. In fact, some studies have found evidence that discrimination against Black people in rental markets is statistical in nature, as landlords use race as a proxy for income. One study found that for Blacks who imply that they are of a higher social class when applying for an apartment, discrimination is virtually not present \citep{hanson}.

\cite{kakar} conduct a similar analysis for hosts in San Francisco as \cite{wang} in Oakland, and \cite{edelman} in New York City. They code the race, gender, self-identified sexual orientation, and whether the host is a couple from the host profile pictures. Since each picture required manual coding, they identify only 800 out of 6,000 active listings in San Francisco as of 2015. The researchers find that Asian hosts charge 8\% lower prices relative to White hosts for comparable listings, controlling for neighborhood property values from Trulia, area demographics from the Census, and occupancy rates purchased from a third party as proxies for desirability or attractiveness of the locations. The price disparity is 10\% for Hispanic hosts, but becomes insignificant when adding a control for occupancy rates. The price discrepancy for Asian hosts is persistent at 8\%. 

Several audit studies have also examined discrimination on the other side of the market - those who demand, rather than supply, listings on Airbnb. These studies follow the canonical model of the \cite{bertrand} study, which sent identical resumes to employers, varying only whether the names were distinctively White or Black. 

\cite{cui} conducted an audit study to measure discrimination against Airbnb guests. They created fake guest accounts with identical profiles but with different names, either distinctively White or distinctively Black. In the first round of their experiment, they sent out requests for accommodation from a set of accounts with no reviews, as well as a set of accounts with one positive review. In the second round, the accounts were modified to have one negative review. They found that guests with White-sounding names were accepted on average 19 percentage points more often than those with African American-sounding names when the guest accounts had no reviews, but that the presence of a single review, whether positive or negative, rendered the acceptance rates statistically indistinguishable \citep{cui}.

In a more recent audit study, \cite{edelman2} measured discrimination against Airbnb guests. They created fake guest accounts that differed only by name and inquired about the availability of listings across five cities. They found that requests for reservations by guests with distinctively Black names were 16\% less likely to be accepted by hosts than identical guests with distinctively White names. The estimated cost to the median host who rejects a guest on the basis of race was a loss of between \$65 -- \$100 of revenue \citep{edelman2}.











\begin{comment}
%\citep{yinger1}
%Landlords renting out apartments discriminate both because of their own prejudice and in response to the prejudice of their white renters \citep{ondrich}.

Structurally, African-Americans were denied Federal Housing Adminstration mortgages at the low interest rates that were offered to white families, redlining districts , predatory , among many other structural moving north during the Great Migration were met with  Shut out from One reason is  
Many efforts have been made to curb discrimination in the housing sector against African-Americans. Landmark federal legislation such as the Fair Housing Act of 1968 prohibits housing discrimination based on race, the enforcement of anti-discrimination legislation is difficult on the local level. Residential preferences, differences in family structure and availability of affordable housing contribute to these disparities. Discrimination in housing has also been cited as one of the primary causes of these inequities. 

%Even though the accurate identification and measurement of discrimination by social scientists is vital to creating policies and statutes to combat it, measuring discrimination is difficult. Unobservable variables in the error term make it hard to isolate the effect of discrimination on the outcome variable of interest. Audit studies are one way that researchers can isolate the effect of race, sex, or other demographic on the outcome of interest. However, these types of experiments are not always possible due to the large organizational, manpower, or time costs associated with them. In the absence of an experimental set-up, regression models with a carefully chosen set of controls can aid in the accurate measurement of discrimination.  
Discrimination is difficult to measure. In the real world. Economists and other social scientists have long been concerned with the fact that minorities, especially African-Americans, have experienced pervasively lower living standards in the United States. One potential cause of this is discrimination in the housing market. 

Moreover, many small players have entered these markets who would have otherwise been unable to participate in traditional markets. Managing a room or home with Airbnb has much lower barriers to entry than being the landlord of a large apartment building. In just the 10 years since its founding, Airbnb has surpassed Marriott nearly three-fold in the number of rooms offered worldwide \citep{sharing}. 
\end{comment}

%As more people have entered these new markets, they have become increasingly dependent on the supplementary income they provide. Hosting with Airbnb, a platform that allows people to rent out their apartment, house, or single room to short-term lodgers, is one such opportunity. A 2017 report released by Airbnb states that in rural areas, hosts get as much as 5 - 20\% of their income from their listing \citep{rural}. Airbnb's fastest growing demographic of hosts, women over 60 years of age, earn \$6,000 a year on average from hosting, often relying on that income to supplement retirement savings \citep{elderly}\citep{nyt2}. 

%Some residents of areas of New York City have started relying on hosting with Airbnb to pay for rent or fund retirement \citep{nyt1}. 

%The extent to which hosts have grown to rely on Airbnb as a source of income makes discrimination on the platform a relevant topic of research. The economic consequences of discrimination are substantial - hosts who are discriminated against would face lower demand, have higher vacancies, and earn less revenue from their listing. While one previous paper found evidence of discrimination against New York City hosts using data from 2013, no other more recent or comprehensive research has been done on this type of discrimination on Airbnb. 

%In this paper, I empirically investigate the existence and extent of anti-host discrimination in Airbnb. I start by measuring the effect of host race and sex on the price of the listing and on a constructed measure of host revenue. I use data from a webscrape of around 70,000 Airbnb listings across 7 U.S. cities.\footnote{The scrape includes all of the property, host, and review information on a listing profile. To see what information would be available, see Figures 1-5 for screenshots of a sample listing. All of the information seen on the sample listing is included as variables in the data set.} For each of the 70,000 listings, the race, sex, and age of the host from their profile picture was coded. 

%Next, I construct a measure of host revenue by multiplying the price a host charges by the total number of reviews for that listing (a proxy for the quantity demanded). Using this measure of revenue, I estimate that White female hosts, Black male hosts, Black female hosts, and Asian female hosts lose about \$100-\$300 in revenue over the course of a year as compared to White male hosts who own similar listings. The exact revenue loss depends on the coefficients on price and number of reviews of a particular host.\footnote{See Table 5 and Section 3.2 for the exact effects on revenue.} These effects are statistically significant at the p $<$ .05 level or higher, and significant at the p $<$ .001 level for White females and Black females. There are also negative effects on revenue for Hispanic hosts and Asian males, but they are not significant. In Section 4, I also conduct several robustness checks and show that these results hold across various cities, price ranges, time on the market, and property types.\footnote{See Tables 6, 7 and discussion in Section 4.}

% Understanding discrimination in this new housing market is important because it ties into racial discrepancies in housing widely observed by economists and other social scientists. 

% However, it is difficult to separate the effect of current racial discrimination from the confounding effect of these other economic realities. It is therefore unclear to what extent current discrimination, especially in the housing market, contributes to these long-standing economic disparities. 

%Even though the accurate identification and measurement of discrimination by social scientists is vital to creating policies and statutes to combat it, measuring discrimination is difficult. Unobservable variables in the error term make it hard to isolate the effect of discrimination on the outcome variable of interest. Audit studies are one way that researchers can isolate the effect of race, sex, or other demographic on the outcome of interest. However, these types of experiments are not always possible due to the large organizational, manpower, or time costs associated with them. In the absence of an experimental set-up, regression models with a carefully chosen set of controls can aid in the accurate measurement of discrimination.  

% Economists and other social scientists have long documented the poor housing outcomes for minorities, particularly African-Americans, in the housing market.