\documentclass[11pt, oneside]{article}   	
\usepackage[margin = 1 in]{geometry}                		
\geometry{letterpaper}                   		
%\usepackage[parfill]{parskip}    %Begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				
\usepackage{setspace}								
\usepackage{amssymb}
\doublespacing
%\geometry{footnotesep=2\baselineskip}
\usepackage{longtable}
\usepackage{caption} %Put caption* in a table to remove the enumeration
\usepackage{rotating} % To rotate the reviewer table
\usepackage{natbib}   %activates bibliography
\usepackage [english]{babel} %something for bibliography
\usepackage{verbatim} %to be able to use \begin{comment}
\usepackage{booktabs}
\usepackage{array}
\usepackage{float} 


\begin{document}


\begin{comment}
Options for first sentence of abstract:
\begin{enumerate}
\item The extent of discrimination on Airbnb, especially against hosts, remains poorly researched. 
\item Despite well-publicized efforts by Airbnb to address discrimination on its platform, the discrimination against hosts remains poorly measured by economists. 
\item Even though discrimination against hosts on Airbnb carries serious economic consequences for agents, the issue has remained poorly researched. 
\item Measuring discrimination is challenging because in the absence of an experiment, it requires controlling for an extensive set of covariates. 
\item Little research has been done on the extent of discrimination against hosts on Airbnb because of data restrictions, and difficulty of setting up an experiment. 
\end{enumerate}
\end{comment}


\title{Measuring Discrimination: The Impact of Host Race and Gender on Earnings from Airbnb\footnote
	{I thank Steven D. Levitt for valuable advice. Kirthi Bellamkonda, Jacob Dorn, Michal Dzitko, Sonia Jaffe, Ezra Karger, Sylvia Klosin, Victor Lima, and Kotaro Yoshida provided excellent feedback and comments. Mahathi Ayyagari, Fong Chai, Joseph Day, Melody Jih, Spencer Kang, Cristian Raygoza, Tony Song, Lydia Sum, Putter Thepkanjana, and Leah Umanskiy provided research assistance. All remaining errors are my own. Data was provided by InsideAirbnb.com, founded and maintained by Murray Cox. Airbnb was not consulted in this research. Sentiment analysis would not be possible without Sentimentr and coding by Ben Chaimberg.}}
\author{Anya Marchenko}
\maketitle


\begin{abstract}
Measuring discrimination is challenging because XXX. Racial bias faced by Airbnb hosts is a topic largely underrepresented in economic literature. Earlier research has attempted to measure discrimination against New York City hosts, but was limited by a small sample size and narrow set of controls. I address this issue by using a previously unexploited dataset from a large webscrape of the Airbnb website to measure discrimination. Controlling for a large set of covariates, I estimate that black hosts earn \$5 - 7 less per night, and Asian hosts \$6 - 9 less per night (depending on the sex of the host) than white hosts who post a similar type of listing. In addiiton to price data, I also have data on quantity demanded of hosts' listings. I measure that quantity demanded is also lower for minority hosts, suggesting a demand shift, rather than a supply shift. There is little evidence that these price disparities are due to minority hosts choosing to price their listings lower because of differences in their marginal cost, or offering their listing up for rent for shorter periods of time, than white hosts. I also find little evidence that this effect is due to minority hosts owning listings of worse quality. Overall, among the hypotheses I test, discrimination is the most convincing explanation for this persistent price disparity. 
\end{abstract}


\doublespacing
\section{Introduction}
\input{1_intro_lit}

\section{Data}
\input{2_data}

\section{Results}
\input{3_results}

\section{Testing Alternative Hypotheses}
\input{4_hypotheses}

\section{Conclusion \& Further Work}
\input{5_conclusion}
\newpage

\bibliographystyle{elsarticle-harv}
\bibliography{bibliography2}

\newpage
\input{full_tables.tex}

\newpage
\section{Appendix}
\subsection{Data Appendix}
\input{6_data_appendix}

\newpage
\subsection{Figures}
\input{full_figures.tex}

\newpage


\begin{comment} 
In this section, I consider alternative explanations for the price differences I found between minority and white hosts. In particular, I examine three relevant mechanisms that are not discrimination that could explain my results. I will then argue that these mechanisms would be insufficient in doing so. 

\textbf{2. Price observed during the scrape is not the price normally set by hosts or observed by guests}

The prices I used in my data analysis were prices from one particular day in 2015-2016. I ran my regressions on the assumption that this is the price that hosts set and that guests observe that drives guest booking decisions and host revenue outcomes. However, imagine that for one day, all of the white people on Airbnb raise their prices. That day, the scrape happens to take place, and the next day, the prices of White hosts all go back down. Then, the price that I observed in my data for White hosts would be high even though it doesn't incorporate real demand differences between races nor is tied to listing characteristics or host quality. While this may seem like an unlikely scenario, price hikes for the weekend or for holidays like July 4th or New Year's may give rise to a similar situation if black hosts change their prices differently than White hosts. 

TO-DO - Check price time series data to prove that prices don't move around that much during the month/year. 

\textbf{3. Data clean-up disproportionately dropped lower-priced listings of White hosts or higher-priced listings of minority hosts}

During my analysis, I left out hosts that had no profile picture. If hosts are aware of the potential effects of discrimination, minority hosts might be less likely to include a profile picture. If minority hosts who own higher-priced listings dropped out of the data set in this way, my coefficients might be biased downward because the sample doesn't include the higher-priced listings owned by minority hosts. A similar thing could have happened when I restricted my data set to listings with a price per night of less than \$800, and to listings owned by hosts who owned fewer than 20 listings total. If those hosts who owned a lot of listings or charged wildly high prices per night were disproportionately black, Hispanic, or Asian, I'd see a similar downward bias on my coefficients.

TO-DO - Examine who I am dropping when I do data-clean up. 

************Garbage
After controlling for listing characteristics, host characteristics, and the neighborhood location of the Airbnb, and time on the market, I find that all host categories, but especially black male hosts, white female hosts, black female hosts, and Asian female hosts, for whom the result is statistically significant at at least the p < .01 level, earn approximately \$200 less during the course of their listing than white male hosts.  will earn \$190 - \$284 less revenue from their Airbnb over the course of the posting relative to their white male peers. The effect is statistically significant at the p < .001 level for white female and black female hosts, and significant at the p < .01 level for black male hosts and Asian female hosts. While there is a large downward effect on revenue for Hispanic male, Hispanic female, and Asian male hosts, it does not persist after controlling for listing and host characteristics. Contrary to what one would expect from discrimination literature, out of the groups for whom I could measure discrimination, black male fared the least poorly, earning \$190 less than white male hosts over the course of their listing?s lifetime. Women as a whole, regardless of race, do worse than black men. Asian women earn \$232.6 less in revenue and white women earn \$272 less in revenue than white male peers. Black women hosts fare the worst out of any of the groups considered, earning \$283.6 less than white men over the course of their Airbnb listing. 

white male reviewers gave lower reviews only to Asian female, with a .074-unit decrease relative to white male hosts. Black male guests gave white female hosts .207 units, two white male hosts .624 lower, Asian men .517 units higher quality reviews than they gave white men. White females gave lower quality reviews only to Asian women at a rate of .099 units less. Black female reviewers gave Airbnbs owned by two black women an entire valence point, 1.005 units better reviews than white male hosts, but rated Hispanic women .647 units lower. Asian females rated Black male hosts .358 units worse than white male hosts. 


TO-DO: Add Levitt and Fryer? Black names paper
List (2004) found a similar result at baseball card shows, with Black sellers getting offer 3-30\% worse than White sellers. 

Becker explains, ``If someone has a `taste for discrimination', he must act as if he were willing to forfeit income in order to avoid certain transactions; it is necessary to be aware of the emphasis on the words `as if'" (Becker 16).While market discrimination harms the discriminated group because it lowers their wages, taste discrimination can also harm the person discriminating, since they might now be paying more for the same good or service - whether in opportunity cost or price -  because they prefer not to interact with the discriminated group. 
Another type of discrimination laid out by Becker is taste discrimination, in which people ``prefer" not to interact with certain groups. This type of taste discrimination that is based on a general dislike could show up in the reviews that are left on host profiles. If a guest stays with a host against whom they are prejudiced, they may leave a worse review or rating, a shorter review, or no review at all, than a comparable stay with a white host. 

********former introduction

When Dyne Suh was minutes away from arriving at the Airbnb she had booked for a weekend getaway, she received a cancellation notice from the host. Left stranded in a snowstorm, Suh offered to pay extra for her stay. The host, through a series of racist messages on the Airbnb app, revealed that she had cancelled because Suh appeared Asian.\cite{diane}  

This example from February 2017 is an extreme case of overt racism, and ended in Airbnb permanently banning the host from the platform. Yet, over the past several years, users have reported more subtle discrimination on Airbnb through social media stories of hosts cancelling or rejecting guests.\cite{nyt1} After being under fire for most of the year, Airbnb updated its Discrimination Policy in September 2016, increasing instant bookings (the opportunity for guests to book without waiting for host approval) and making host profile pictures smaller.\cite{nyt2} 

Sharing economies platforms create a particularly complex environment for regulating discrimination. On the one hand, agents are constrained by certain features of the user interface - if Airbnb never provided guests with a picture or the name of the host, there would be little opportunity to discriminate. On the other hand, users ultimately have nearly full control of the transactions they engage in. For example, drivers on Uber can choose not to accept certain trips or turn the app on or off at their convenience. 

However, these stories of discrimination against \textit{guests} provide only anecdotal evidence for the larger problem of discrimination in the Airbnb market. The problem of discrimination against \textit{hosts} is not publicized, even though it just as important because it affects the prices, revenues, and sometimes livelihoods of thousands of Airbnb hosts. 
\iffalse %comments out entire section of text
\begin{quotation}
``Suppose there are two groups, designated by $W$ and $N$, with members of $W$ being perfect substitutes in production for members of $N$. In the absence of discrimination and nepotism and if the labor market were perfectly competitive, the equilibrium wage rate of $W$ would equal that of $N$. Discrimination could cause these wage rates to differ; the market discrimination coefficient between $W$ and $N$ [...] is defined as the proportional difference between these wage rates" \end{quotation}
\fi
\end{comment}


\end{document}  