\documentclass[11pt, oneside]{article}   	
\usepackage[margin = 1 in]{geometry}                		
\geometry{letterpaper}                   		
\edef\restoreparindent{\parindent=\the\parindent\relax} % this and the next 2 lines parskip AND indent
\usepackage{parskip}
\restoreparindent
%\usepackage[parfill]{parskip}    %Begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				
\usepackage{setspace}								
\usepackage{amssymb}
\doublespacing
%\geometry{footnotesep=2\baselineskip}
\interfootnotelinepenalty=10000 %prevents long footnotes from overflowing to new page
\usepackage{longtable}
\usepackage{caption} %Put caption* in a table to remove the enumeration
\usepackage{rotating} % To rotate the reviewer table
\usepackage{natbib}   %activates bibliography
\usepackage [english]{babel} %something for bibliography
\usepackage{verbatim} %to be able to use \begin{comment}
\usepackage{booktabs}
\usepackage{array}
\usepackage{float} 
\usepackage{pdflscape} %allows for one page to be landscape (lscape makes word landscape, pdflscape makes page landscape)
\usepackage{threeparttable} %allows tablenotes
\usepackage{amsmath}
\usepackage{import} % to use import commands relative to the file path
\usepackage[autolanguage]{numprint} % prints numbers with thousandths separator 
\usepackage{dirtytalk} % quotations shortcut

\begin{document}
		
	\title{The Impact of Host Race and Gender on Prices on Airbnb\footnote
		{I thank Steven D. Levitt for valuable advice. Kirthi Bellamkonda, Jacob Dorn, Michal Dzitko, Michael Galperin, Sonia Jaffe, Ezra Karger, Sylvia Klosin, Victor Lima, and Kotaro Yoshida provided helpful feedback and comments. Abdallah Aboelela, Melody Jih, and Thiago Resende provided excellent research assistance. I thank Mahathi Ayyagari, Melody Jih, Fong Chai, Lydia Sum, Joseph Day, Leah Umanskiy, Cristian Raygoza, Putter Thepkanjana, Spencer Kang, and Tony Song for coding host demographics. All remaining errors are my own. Data was provided by InsideAirbnb.com, founded and maintained by Murray Cox. Airbnb was not consulted in this research.}}
	\author{Anya Marchenko\footnote{University of Chicago, Becker Friedman Institute}}
	\maketitle
	
	\begin{abstract}
		This study investigates the impact of host race and gender on Airbnb property prices. I use an existing dataset of Airbnb listings and visually inspect 70,000 host profile pictures to code host demographics. I estimate that Asian hosts earn 4 -- 5\%, and Black male hosts 3\%, less than White males for the same type of property. However, controlling for more observables weakens the effects, requiring a cautious interpretation of these point estimates. I use two proxies for the number of bookings a listing has to estimate whether a demand or supply shift is responsible for the price disparity. I find that despite the lower prices they charge for listings, minority hosts face lower demand. These findings are consistent with, but not conclusive of, the presence of discrimination. 
		\\\\
		\textit{Keywords}: Airbnb; Discrimination; Race; Online marketplace
		
	\end{abstract}
	%		 the point estimates suggest a price disparity, 
	
	\newpage
	
	\singlespacing
	\section{Introduction}
	\input{1_intro_lit}
	\label{intro}

\newpage
	\section{Data}
	\input{2_data}
	\label{data}
	
	\section{Empirical Approach}
	\input{3_empirical_approach}
	\label{empirical}
	
	\section{Results}
	\input{4_results}
	\label{results}
		
	\section{Conclusion \& Further Work}
	\input{5_conclusion}
	\label{conclusion}
	\newpage
	
	\bibliographystyle{elsarticle-harv}
	\bibliography{bibliography2}
	
	\newpage
	\input{full_figures}
	
	\newpage
	\input{full_tables}

	
	
	\begin{comment}
		
	In this section, I consider alternative explanations for the price differences I found between minority and white hosts. In particular, I examine three relevant mechanisms that are not discrimination that could explain my results. I will then argue that these mechanisms would be insufficient in doing so. 
	
	\textbf{2. Price observed during the scrape is not the price normally set by hosts or observed by guests}
	
	The prices I used in my data analysis were prices from one particular day in 2015-2016. I ran my regressions on the assumption that this is the price that hosts set and that guests observe that drives guest booking decisions and host revenue outcomes. However, imagine that for one day, all of the white people on Airbnb raise their prices. That day, the scrape happens to take place, and the next day, the prices of White hosts all go back down. Then, the price that I observed in my data for White hosts would be high even though it doesn't incorporate real demand differences between races nor is tied to listing characteristics or host quality. While this may seem like an unlikely scenario, price hikes for the weekend or for holidays like July 4th or New Year's may give rise to a similar situation if black hosts change their prices differently than White hosts. 
	

	\textbf{3. Data clean-up disproportionately dropped lower-priced listings of White hosts or higher-priced listings of minority hosts}
	
	During my analysis, I left out hosts that had no profile picture. If hosts are aware of the potential effects of discrimination, minority hosts might be less likely to include a profile picture. If minority hosts who own higher-priced listings dropped out of the data set in this way, my coefficients might be biased downward because the sample doesn't include the higher-priced listings owned by minority hosts. A similar thing could have happened when I restricted my data set to listings with a price per night of less than \$800, and to listings owned by hosts who owned fewer than 20 listings total. If those hosts who owned a lot of listings or charged wildly high prices per night were disproportionately black, Hispanic, or Asian, I'd see a similar downward bias on my coefficients.
	
	\iffalse %comments out entire section of text
	\begin{quotation}
	``Suppose there are two groups, designated by $W$ and $N$, with members of $W$ being perfect substitutes in production for members of $N$. In the absence of discrimination and nepotism and if the labor market were perfectly competitive, the equilibrium wage rate of $W$ would equal that of $N$. Discrimination could cause these wage rates to differ; the market discrimination coefficient between $W$ and $N$ [...] is defined as the proportional difference between these wage rates" \end{quotation}
	\fi
	\end{comment}
	
	
\end{document}  
